D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-03 ootavacuous.tex
Use directives for litmus-test listings December 3rd
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{listing}[tbp]
\begin{verbatim}
 1 C oota-causality-1
 2 {
 3   [x] = 0;
 4   [y] = 0;
 5 }
 6
 7 P0(volatile atomic_int *x, volatile atomic_int *y) {
 8   int r1 = atomic_load_explicit(x, memory_order_relaxed);
 9   if (r1 >= 0)
10     atomic_store_explicit(y, 1, memory_order_relaxed);
11 }
12
13 P1(volatile atomic_int *x, volatile atomic_int *y) {
14   int r2 = atomic_load_explicit(y, memory_order_relaxed);
15   atomic_store_explicit(x, r1, memory_order_relaxed);
16 }
17
18 exists(0:r1=1 /\ 1:r2=1)
\end{verbatim}
\caption{Causality Test Case 1}
\label{lst:Causality Test Case 1}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
 1 C oota-causality-2
 2 {
 3   [x] = 0;
 4   [y] = 0;
 5 }
 6
 7 P0(volatile atomic_int *x, volatile atomic_int *y) {
 8   int r1 = atomic_load_explicit(x, memory_order_relaxed);
 9   int r2 = atomic_load_explicit(x, memory_order_relaxed);
10   if (r1 == r2)
11     atomic_store_explicit(y, 1, memory_order_relaxed);
12 }
13
14 P1(volatile atomic_int *x, volatile atomic_int *y) {
15   int r3 = atomic_load_explicit(y, memory_order_relaxed);
16   atomic_store_explicit(x, r3, memory_order_relaxed);
17 }
18
19 exists(0:r1=1 /\ 0:r2=1 /\ 1:r3=1)
\end{verbatim}
\caption{Causality Test Case 2}
\label{lst:Causality Test Case 2}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
 1 C oota-causality-3
 2 {
 3   [x] = 0;
 4   [y] = 0;
 5 }
 6
 7 P0(volatile atomic_int *x, volatile atomic_int *y) {
 8   int r1 = atomic_load_explicit(x, memory_order_relaxed);
 9   int r2 = atomic_load_explicit(x, memory_order_relaxed);
10   if (r1 == r2)
11     atomic_store_explicit(y, 1, memory_order_relaxed);
12 }
13
14 P1(volatile atomic_int *x, volatile atomic_int *y) {
15   int r3 = atomic_load_explicit(y, memory_order_relaxed);
16   atomic_store_explicit(x, r3, memory_order_relaxed);
17 }
18
19 P2(volatile atomic_int *x, volatile atomic_int *y) {
20   atomic_store_explicit(x, 2, memory_order_relaxed);
21 }
22
23 exists(0:r1=1 /\ 0:r2=1 /\ 1:r3=1)
\end{verbatim}
\caption{Causality Test Case 3}
\label{lst:Causality Test Case 3}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
 1 C oota-causality-4
 2 {
 3   [x] = 0;
 4   [y] = 0;
 5 }
 6
 7 P0(atomic_int *x, atomic_int *y) {
 8   int r1 = atomic_load_explicit(x, memory_order_relaxed);
 9   atomic_store_explicit(y, r1, memory_order_relaxed);
10 }
11
12 P1(atomic_int *x, atomic_int *y) {
13   int r2 = atomic_load_explicit(y, memory_order_relaxed);
14   atomic_store_explicit(x, r2, memory_order_relaxed);
15 }
16
17 exists(0:r1=1 /\ 1:r2=1)
\end{verbatim}
\caption{Causality Test Case 4}
\label{lst:Causality Test Case 4}
\end{listing}

>>>>

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-1.litmus @@
\end{verbatim}
\caption{Causality Test Case 1}
\label{lst:Causality Test Case 1}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-2.litmus @@
\end{verbatim}
\caption{Causality Test Case 2}
\label{lst:Causality Test Case 2}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-3.litmus @@
\end{verbatim}
\caption{Causality Test Case 3}
\label{lst:Causality Test Case 3}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-4.litmus @@
\end{verbatim}
\caption{Causality Test Case 4}
\label{lst:Causality Test Case 4}
\end{listing}
